Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
updated figure 6

\begin{figure}[htp]
  \begin{minipage}{0.6\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
  of vesicle hydrodynamics in an extensional flow.  At a fixed Hamaker
  constant $H=0.7$ and adhesion length scale $\delta=0.4$.  For small
  extensional rates, the doublet structure is not broken (blue marks),
  while at large extensional rates, the doublet is broken (red marks).
  {\em Right}: The definition of the inclination angle.  An inclination
  angle of $\pi$ indicates a doublet whose long axis is parallel to the
  converging direction, while an inclination angle of $\pi/2$ indicates
  a doublet whose short axis is parallel to the converging direction.
  The square mark is a stagnation point while the round point is located
  at the center of the vesicle.}
\end{figure}

>>>>

\begin{figure}[htp]
  \begin{minipage}{0.6\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
  of vesicle hydrodynamics in an extensional flow with a fixed Hamaker
  constant $H=0.7$ and adhesion length scale $\delta = 0.4$.  For small
  extensional rates, the doublet structure is not broken (blue marks),
  while at large extensional rates, the doublet is broken (red marks).
  The size of the round blue marks indicate the final inclination angle
  with the larger dots rotation less ($\theta=pi$) and the smaller dots
  rotating more ($\theta = pi/2$).  A square mark is used for
  simulations that did not result in a steady-state inclination angle in
  the given time horizon.  {\em Right}: The definition of the
  inclination angle.  An inclination angle of $\pi$ indicates a doublet
  whose long axis is parallel to the converging direction, while an
  inclination angle of $\pi/2$ indicates a doublet whose short axis is
  parallel to the converging direction.  The square mark is a stagnation
  point while the round point is located at the center of the vesicle.}
\end{figure}
